
---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# lifetableprojection

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

This package aims to create a shiny webapp to make lifetable projections available to users which are not familiar with R. The web application allows to upload data, validate it and conduct lifetable projections.

## Installation

You can install the development version of lifetableprojection from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("cimentadaj/lifetableprojection")
```

## Example

This is a basic example which shows you how to solve a common problem:


```{r example, eval = FALSE}
library(lifetableprojection)
run_app()
```
